% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./images/} }

% Please include a clear, concise, and descriptive title
\title{Teamwork Review} 

% Please do not change the subtitle
\subtitle{COMP150 - Teamwork Review}

% Please put your student number in the author field
\author{1507516}

\begin{document}

\maketitle

\abstract{%Abstract }

\section{Introduction}

This is a reflective report that proposes two teamwork weaknesses that occurred during the comp150 group game project, and suggests how these issues could be overcome for future projects.

\section{Key Teamwork Skills}
\subsection{Teamwork Weakness One: Communication}

Throughout this project our team members did not actively communicate outside of class, we seemed to only rely on Trello to communicate the work that was being done. This was partly due to that I did not feel the need to communicate when we were working on the project, partly due to that we all had our own separate parts of the game we needed to work on. However I do think that if we did communicate more over the project, that would of increased my motivation to work on the project.

To try and overcome this issue in future development projects I will try to actively follow the Agile/scrum way of working and tell my team what I am working on each day. This will hopefully motivate my team members to work on the game that day aswell.

\subsection{Teamwork Weakness Two: Motivation and Support}

Quite often during the development of the game I lost motivation to work on the game, this was due to several factors, the main one was feeling that I did not have a sufficient understanding of C++ to be able to implement the parts of the game I was assigned, when my team members seemed to have no problem. Furthermore I did not ask for support when I encountered these problems as I felt that it was my responsibility to try and complete the parts that I was assigned.

In the future I will try to overcome these issues by creating a pull request on any work that I am stuck on, as this assignment I was unable to do so, because the repository was owned by one of the team members. Furthermore I will try and consult more with my team members when I run into problems, and vice-versa.

\section{Conclusion}

Overall these are two important issues when working in a team, and improving them would have increased the quality and quantity of the work. So for future projects I will try and overcome these issues by following the proposed solutions.

%\bibliographystyle{ieeetr}
%\bibliography{comp150_Agile}

\end{document}
